---
title: "Attempt to calculate LENA accuracy for ling/nonling"
author: "AC"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(scales)
library(caret)
```

## Read data in

NOTE: This section cannot be reproduced because it requires access to data that haven't been shared.

```{r read-data,eval=F}
read.csv("result_final_lisa.csv")->metadata
metadata[1,]

csvs=dir("../Raw_Data/its_to_csv/",pattern="csv")

#count_present=NULL
all_segments=NULL
# extract info from csv's
for(thisits in levels(metadata$filename)){
  csv=grep(thisits,csvs)
  #count_present=c(count_present,length(csv))
  if(length(csv)==1){
    #read in full csv
    read.csv(paste0("../Raw_Data/its_to_csv/",csvs[csv]))->thisdat
    
    #select down to the lines used in zooniverse
    sel_segments_start=metadata[metadata$filename==thisits,"Starttime"]
    sel_segments_dat=thisdat[thisdat$startTime %in% sel_segments_start,]
    
    #the following is NOT right: we take the data in even if there is a mismatch in start/end time
    if(dim(sel_segments_dat)[1]!=length(sel_segments_start)) print(paste(thisits, csvs[csv], "have line mismatches:",dim(sel_segments_dat)[1],length(sel_segments_start)))
    if(dim(sel_segments_dat)[1]>0){
      
     #derive LENA classification at the segment level
    sel_segments_dat$LENA_type=NA
      #if ling info contained, then ling
    sel_segments_dat$LENA_type[is.na(sel_segments_dat$LENA_type) & sel_segments_dat$childUttLen>0 & !is.na(sel_segments_dat$childUttLen)]<-"Can/non-can"
      #elsif there is crying
    sel_segments_dat$LENA_type[is.na(sel_segments_dat$LENA_type) &  !is.na(sel_segments_dat$endCry1)]<-"Crying"
     #elsif there is fixed then laughing
    sel_segments_dat$LENA_type[is.na(sel_segments_dat$LENA_type) &  !is.na(sel_segments_dat$endVfx1)]<-"Laughing"
    #else junk
    sel_segments_dat$LENA_type[is.na(sel_segments_dat$LENA_type)]<-"Junk"
    
    sel_segments_dat=sel_segments_dat[,c("itsId","startTime", "endTime","LENA_type")]
    
    #combine with lab annotation
    sel_segments_dat=merge(sel_segments_dat,metadata[metadata$filename==thisits,],by.x="startTime",by.y="Starttime")
    
    #add to full spreadsheet
    all_segments=rbind(all_segments,sel_segments_dat)     
    } 

    
  } else print(paste(thisits,"not found"))
}
write.csv(all_segments,"LENA_type_lab.csv",row.names = F)
```

## Correspondence between LENA & lab annotation at the level of segments

Here we look at to what extent LENA and lab annotations match at the level of individual segments. Each data point is one segment (one "vocalization").


```{r}

read.csv("LENA_type_lab.csv")->all_segments

## NOOOOOOOTE !!!! REMOVING Num_Agreement < 2
all_segments=all_segments[all_segments$Num_Agreement>=2,]

# create lab column with easier to read correspondance
all_segments$lab<-as.character(all_segments$Major_Choice)
all_segments$lab[all_segments$lab=="Non-canonical syllables"]<-"Non-Canonical"
all_segments$lab[all_segments$lab=="Canonical syllables"]<-"Canonical"
all_segments$lab[all_segments$lab=="Words"]<-"Canonical"  #!!! why didn't I need this before??
all_segments$lab[all_segments$lab %in% c("Don't mark","None")]<-"Junk"

#collapse acros can and non-can
all_segments$lab[all_segments$lab %in% c("Non-Canonical","Canonical")]<-"Can/non-can"


table(all_segments$lab)
table(all_segments$LENA_type)

all_segments$lab=factor(all_segments$lab,levels=c("Can/non-can","Laughing","Crying","Junk"))
all_segments$LENA_type=factor(all_segments$LENA_type,levels=c("Can/non-can","Laughing","Crying","Junk"))


mycf=confusionMatrix(all_segments$lab, all_segments$LENA_type, dnn = c("Lab","LENA"))
conf_tab=mycf$table
# this package uses sensitivity & specificity
#Sensitivity=recall
#Specificity=precision
mycf
```

### Precision

Precision means: If a segment was called X by LENA, what proportion of the time was it called X by lab coders?


```{r prec2}

colsums=colSums(conf_tab)
my_conf_tab=conf_tab
for(i in 1:dim(my_conf_tab)[2]) my_conf_tab[,i]=my_conf_tab[,i]/colsums[i]
colSums(my_conf_tab)
prop_cat=data.frame(my_conf_tab*100) #generates precision because columns
prop_cat$id=paste(prop_cat$Lab,prop_cat$LENA)
colnames(prop_cat)[3]<-"pr"
data.frame(conf_tab)->stall
stall$id=paste(stall$Lab,stall$LENA)
stall=merge(stall,prop_cat[c("id","pr")])
ggplot(data = stall, mapping = aes(y = Lab, x=LENA)) +
 geom_tile(aes(fill= rescale(pr)), colour = "white") +
  geom_text(aes(label = paste(round(pr),"%")), vjust = -1) +
  geom_text(aes(label = Freq), vjust = 1) +
  scale_fill_gradient(low = "white", high = "red", name = "Proportion") +
     theme(legend.position = "none") +
  xlab("LENA") + ylab("Lab") +
  ggtitle("Precision")+theme(text = element_text(size=20),
        axis.text.x = element_text(angle=90, hjust=1))

```

### Recall

Recall means: If a segment was called X by lab coders, what proportion of the time was it called X by LENA coders?


```{r recall2}

prop_cat=data.frame(conf_tab/rowSums(conf_tab)*100)  #generates recall because rows
prop_cat$id=paste(prop_cat$Lab,prop_cat$LENA)
colnames(prop_cat)[3]<-"rec"
data.frame(conf_tab)->stall
stall$id=paste(stall$Lab,stall$LENA)
stall=merge(stall,prop_cat[c("id","rec")])
ggplot(data = stall, mapping = aes(y = Lab, x=LENA)) +
 geom_tile(aes(fill= rescale(rec)), colour = "white") +
  geom_text(aes(label = paste(round(rec),"%")), vjust = -1) +
  geom_text(aes(label = Freq), vjust = 1) +
  scale_fill_gradient(low = "white", high = "red", name = "Proportion") +
     theme(legend.position = "none") +
  xlab("LENA") + ylab("Lab") +
  ggtitle("Recall")+theme(text = element_text(size=20),
        axis.text.x = element_text(angle=90, hjust=1))

```



